Human-level control through deep reinforcement learning

### 2018-01-02 article/article.tex
[Article] Add 2 plots: average Q-values and score per episode

  \todo{Plots avec les erreurs d'apprentissage (pas de cross-val)}

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{figures/dqn_uniform}
  \caption{(Left) Total score per episode during learning phase, smoothed using a moving average with a window of size 2000.
     (Right) Estimation of Q, averaged across actions, for each batch during learning phase and smoothed using a moving average
      with a window of size 2000.}
\end{figure*}
